### 2024-11-25 paper/Cover_letter_Indecisions.tex
final changes for JNP

We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{Indecision under time pressure arises from suboptimal switching behaviour}}, for publication in \emph{PLOS Computational Biology}.

@@

@@

Han L.J. van der Maas, University of Amsterdam, H.L.J.vanderMaas@uva.nl 

@@

Martin Wiener, George Mason University, mwiener@gmu.edu

@@

>>>>

We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{Indecision under time pressure arises from suboptimal switching behaviour}}, for publication in \emph{Journal of Neurophysiology}.

@@

Laurence Maloney, New York University, laurence.maloney@nyu.edu

@@

Heather Neyedli, Dalhouse University, hneyedli@dal.ca
Todd Hudson, New York University, Todd.Hudson@nyulangone.org

@@

@@

\noindent \textcolor{myudblue}{EDITOR SUGGESTIONS}
Monica Perez
